A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-14 manuscript.Rmd
added two more ideas

<!--AB: add some text explaining what to once the final data is available-->

>>>>

<!--AB: add some text explaining what to once the final data is available. What parts have to be replaced in the code and in the project structure; also recommend tagging the different versions with releases. Do we have functions in repro to do this? Can we have something like repro::release("preprint") or repro::release("preregistration") -- that would be nice! -->
